`r paste("Experiment", params$experiment)`

### 2018-11-05 _analyze.Rmd
Edit figure axes and labels

```{r gamma-performance-plot}
p_gamma_p <- dat_metrics %>%
  ggplot(aes(p, gamma)) +
  geom_vline(xintercept = .25, col = NA) + # Ensure limits
  geom_vline(xintercept = 1, col = NA) + # Ensure limits
  geom_hline(yintercept = 0, lty = 2, size = .33) +
  geom_point(shape = 21, fill = "white", alpha = .75) +
  geom_smooth(method = lm, col = "black", size = .75, alpha = .33) +
  scale_x_continuous(breaks = c(.25, .5, .75, 1)) +
  labs(
    x = "Proportion correct",
    y = "Gamma"
  )
p_gamma_p
```

@@

```{r bias-calculate}
dat_bias <- dat %>%
  # Rescale confidence to 0-1 scale
  mutate(con_01 = ifelse(exp != 5, con6 / 5, con / 10)) %>%
  group_by(exp, subject) %>%
  summarise(
    p = mean(accuracy, na.rm = T),
    con_01 = mean(con_01, na.rm = T)
  ) %>%
  mutate(bias = con_01 - p)
```

@@

```{r bias-summary-test}
dat_bias %>%
  group_by(exp) %>%
  summarise(
    mean = mean(bias, na.rm = T),
    n = n(),
    se = sd(bias, na.rm = T) / sqrt(n),
    NAs = sum(is.na(bias))
  ) %>%
  kable(digits = 3)
t.test(dat_bias$bias)
```

@@

```{r bias-plot-performance}
p_bias_p <- dat_bias %>%
  ggplot(aes(p, bias)) +
  geom_vline(xintercept = .25, col = NA) + # Ensure limits
  geom_vline(xintercept = 1, col = NA) + # Ensure limits
  geom_hline(yintercept = 0, lty = 2, size = .33) +
  geom_point(shape = 21, alpha = .75, fill = "white") +
  geom_smooth(method = lm, col = "black", size = .75, alpha = .33) +
  scale_x_continuous(breaks = c(.25, .5, .75, 1)) +
  labs(
    x = "Proportion correct",
    y = "Bias"
  )
p_bias_p
```

```{r bias-performance-correlate}
# fit_bias <- lm(bias ~ scale(p), data = dat_bias)
# summary(fit_bias)
cor.test(dat_bias$bias, dat_bias$p)
```

>>>>

```{r gamma-performance-plot}
p_gamma_p <- dat_metrics %>%
  ggplot(aes(p, gamma)) +
  geom_vline(xintercept = .25, col = NA) + # Ensure limits
  geom_vline(xintercept = 1, col = NA) + # Ensure limits
  geom_hline(yintercept = 0, lty = 2, size = .33) +
  geom_point(shape = 21, fill = "white", alpha = .75) +
  geom_smooth(method = lm, col = "black", size = .75, alpha = .33) +
    scale_x_continuous(breaks = c(.25, .5, .75, 1), 
                     limits = c(.25, 1), expand = expand_scale(add = .01)) +
  labs(
    x = "Proportion correct",
    y = "Gamma"
  )
p_gamma_p
```

@@

```{r bias-calculate}
dat_bias <- dat %>%
  # Rescale confidence to 0-1 scale
  mutate(con_01 = ifelse(exp != 5, con6 / 5, con / 10)) %>%
  group_by(subject) %>%
  summarise(
    p = mean(accuracy, na.rm = T),
    con_01 = mean(con_01, na.rm = T)
  ) %>%
  mutate(bias = con_01 - p)
```

@@

```{r bias-summary-test}
dat_bias %>%
  summarise(
    mean = mean(bias, na.rm = T),
    n = n(),
    se = sd(bias, na.rm = T) / sqrt(n),
    NAs = sum(is.na(bias))
  ) %>%
  kable(digits = 3)
t.test(dat_bias$bias)
```

@@

```{r bias-plot-performance}
p_bias_p <- dat_bias %>%
  ggplot(aes(p, bias)) +
  geom_hline(yintercept = 0, lty = 2, size = .33) +
  geom_point(shape = 21, alpha = .75, fill = "white") +
  geom_smooth(method = lm, col = "black", size = .75, alpha = .33) +
  scale_x_continuous(breaks = c(.25, .5, .75, 1), 
                     limits = c(.25, 1), expand = expand_scale(add = .01)) +
  labs(
    x = "Proportion correct",
    y = "Mean confidence - proportion correct"
  )
p_bias_p
```

```{r bias-performance-correlate}
cor.test(dat_bias$bias, dat_bias$p)
```
